---
title: "Basic example"
format: html
---

Below is an example showing the basic usage of all the package's functions.

## Set up

Import the package.

```{r}
library(bamboo)
```

## Data import

Import the built-in dataset with simulated unbalanced panel data.

```{r}
data(production)
```

## Panel data structure analysis

The first group of functions is designed to analyze the structure of the panel.

```{r}
describe_dimensions(production, index = c("firm", "year"))
```

```{r}
describe_balance(production, index = c("firm", "year"))
```

```{r}
describe_periods(production, index = c("firm", "year"))
```

```{r}
plot_periods(production, index = c("firm", "year"))
```

```{r}
describe_patterns(production, index = c("firm", "year"))
```

```{r}
plot_patterns(production, index = c("firm", "year"))
```

## Missing values analysis

The second group of functions is aimed at analyzing missing values, taking into account the nature of panel data.

```{r}
plot_missing(production, index = c("firm", "year"))
```

```{r}
summarize_missing(production, index = c("firm", "year"))
```

```{r}
describe_incomplete(production, index = "firm")
```

## Numeric variables analysis

The third group of functions is aimed at analyzing numeric variables, taking into account the nature of panel data.

```{r}
summarize_numeric(production)
```

```{r}
summarize_numeric(production, group = "year")
```

```{r}
plot_heterogeneity(production, select = "sales", group = "year")
```

```{r}
decompose_numeric(production, index = "firm")
```

## Factor variables analysis

The last group of functions is aimed at analyzing numeric variables, taking into account the nature of panel data.

```{r}
decompose_factor(production, index = "firm")
```

```{r}
summarize_transition(production, select = "industry", index = c("firm", "year"))
```