---
title: "Smart example"
format: html
---

Almost all of the package's functions require full or partial specification of a panel structure. To avoid repeating the same steps over and over again, the package allows you to pre-define the panel structure. Examples shown below are simplified by this approach.

## Set up

Import the package.

```{r}
library(bamboo)
```

## Data import

Import the built-in dataset with simulated unbalanced panel data.

```{r}
data(production)
```

Set up a panel structure in advance so that you don't have to do it later each time you use other functions.

```{r}
panel <- make_panel(production, index = c("firm", "year"))
```

## Panel data structure analysis

The first group of functions is designed to analyze the structure of the panel.

```{r}
describe_dimensions(panel)
```

```{r}
describe_balance(panel)
```

```{r}
describe_periods(panel)
```

```{r}
plot_periods(panel)
```

```{r}
describe_patterns(panel)
```

```{r}
plot_patterns(panel)
```

## Missing values analysis

The second group of functions is aimed at analyzing missing values, taking into account the nature of panel data.

You can create a heatmap showing the number of missing values for each variable across all time periods. 

```{r}
plot_missing(panel)
```

Also, you can output the table with brief summary statistics on missing values. 

```{r}
summarize_missing(panel)
```

In addition, you can compare missing values statistics across various entities. 

```{r}
describe_incomplete(panel)
```

## Numeric variables analysis

The third group of functions is aimed at analyzing numeric variables, taking into account the nature of panel data.

If you need to, you can output a table with simple descriptive statistics.

```{r}
summarize_numeric(panel)
```

Descriptive statistics can be grouped by some variable, which does not necessarily have to be a panel identifier.

```{r}
summarize_numeric(panel, group = "year")
```

Heterogeneity between different groups can also be visualized.

```{r}
plot_heterogeneity(panel, select = "sales")
```

For more detailed heterogeneity analysis, numeric variables can be decomposed into between and within components.

```{r}
decompose_numeric(panel)
```

## Factor variables analysis

The last group of functions is aimed at analyzing numeric variables, taking into account the nature of panel data.

Factor variables can be decomposed into between and within components. 

```{r}
decompose_factor(panel)
```

One can also summarize transitions between states of a categorical (factor) variable.

```{r}
summarize_transition(panel, select = "industry")
```