---
title: "Smart example"
format: html
---

Almost all of the package's functions require full or partial specification of a panel structure. To avoid repeating the same steps over and over again, the package allows you to pre-define the panel structure. Examples shown below are simplified by this approach.

## Set up

Import the package.

```{r}
library(bamboo)
```

## Data import

Import the built-in dataset with simulated unbalanced panel data.

```{r}
data(production)
```

Set up a panel structure in advance so that you don't have to do it later each time you use other functions.

```{r}
panel <- make_panel(production, index = c("firm", "year"))
```

## Panel data structure analysis

The first group of functions is designed to analyze the structure of the panel.

```{r}
describe_dimensions(panel)
```

```{r}
describe_balance(panel)
```

```{r}
describe_periods(panel)
```

```{r}
plot_periods(panel)
```

```{r}
describe_patterns(panel)
```

```{r}
plot_patterns(panel)
```

## Missing values analysis

The second group of functions is aimed at analyzing missing values, taking into account the nature of panel data.

```{r}
plot_missing(panel)
```

```{r}
summarize_missing(panel)
```

```{r}
describe_incomplete(panel)
```

## Numeric variables analysis

The third group of functions is aimed at analyzing numeric variables, taking into account the nature of panel data.

```{r}
summarize_numeric(panel)
```

```{r}
summarize_numeric(panel, group = "year")
```

```{r}
plot_heterogeneity(panel, select = "sales")
```

```{r}
decompose_numeric(panel)
```

## Factor variables analysis

The last group of functions is aimed at analyzing numeric variables, taking into account the nature of panel data.

```{r}
decompose_factor(panel)
```

```{r}
summarize_transition(panel, select = "industry")
```