---
title: "Extended example"
format: html
---

Typically, package functions include multiple arguments, the different values ​​of which allow for flexible configuration. Below are various examples demonstrating the package's customization potential.

## Set up

Import the package.

```{r}
library(bamboo)
```

## Data import

Import the built-in dataset with simulated unbalanced panel data.

```{r}
data(production)
```

Set up a panel structure in advance so that you don't have to do it later each time you use other functions.
Note that if `delta` is supplied, the function checks for omitted time periods. If such periods exist, they will be taken into account when other functions work with this argument.

```{r}
panel <- make_panel(production, index = c("firm", "year"), delta = 1)
```

## Creating balanced panel data

The `make_panel()` function also allows to balance panel data using various options:

* keep only entities present in all time periods;

```{r}
balance_entities <- make_panel(production, index = c("firm", "year"), balance = "entities")
```

* keep only time periods where all entities are present;

```{r}
balance_periods <- make_panel(production, index = c("firm", "year"), balance = "periods")
```

* create a row for every entity‑time combination (if `delta` is supplied, the full time sequence including missing periods is used).

```{r}
balance_rows <- make_panel(production, index = c("firm", "year"), delta = 1, balance = "rows")
```

## Panel data structure analysis

```{r}
describe_balance(panel, detail = TRUE, digits = 2)
```

```{r}
describe_periods(panel, digits = 2)
```

```{r}
plot_periods(panel, colors = c("gray", "black"))
```

```{r}
describe_patterns(panel, limits = 3, digits = 2)
```

```{r}
plot_patterns(panel, limits = c(4, 6), colors = c("darkgray", "white"))
```

## Missing values analysis

```{r}
plot_missing(
  panel,
  select = c("labor", "capital"),
  colors = c("black", "white")
)
```

```{r}
summarize_missing(
  panel,
  select = c("labor", "capital"),
  detail = TRUE,
  digits = 2
)
```

```{r}
describe_incomplete(panel, detail = TRUE)
```

## Numeric variables analysis

```{r}
summarize_numeric(
  panel,
  select = c("sales", "labor"),
  group = "year",
  detail = TRUE,
  digits = 2
)
```

```{r}
plot_heterogeneity(
  panel,
  select = "sales",
  group = c("firm", "industry", "year"),
  colors = c("black", "gray")
)
```

```{r}
decompose_numeric(
  panel,
  select = c("sales", "labor"),
  detail = FALSE,
  format = "wide",
  digits = 2
)
```

## Factor variables analysis

```{r}
decompose_factor(panel, select = "industry", format = "long", digits = 2)
```

```{r}
summarize_transition(panel, select = "industry", format = "long", digits = 2)
```