---
title: "Comparison with other packages"
format: html
---

Almost all of this package's functionality can be replicated using individual functions from other packages. However, I believe the main advantage of the `bamboo` package is that it combines all the functions necessary for panel data analysis and implements them in a single format. Below is a comparison with individual functions from other packages.

## Set up

Import packages to compare.

```{r, message=FALSE}
library(bamboo)
library(gplots)
library(modelsummary)
library(pdynmc)
library(xtsum)
```

## Data import

Import the built-in dataset with simulated unbalanced panel data.

```{r}
data(production)
```


## bamboo vs. pdynmc

```{r}
bamboo::plot_patterns(production, index = c("firm", "year"))
```

```{r}
unbalanced <- production[rowSums(!is.na(production[, c("sales", "capital", "labor", "industry")])) > 0, ]
pdynmc::strucUPD.plot(unbalanced, i.name = "firm", t.name = "year")
```

## bamboo vs. modelsummary

```{r}
bamboo::summarize_numeric(production, select = c("capital", "labor"), group = "year")
```

```{r}
modelsummary::datasummary(Factor(year) * (capital + labor) ~ N + Mean + Median + SD + Min + Max, data = production)
```

## bamboo vs. gplots

```{r}
bamboo::plot_heterogeneity(production, select = "sales", group = "year")
```

```{r}
gplots::plotmeans(sales ~ year, production)
```

## bamboo vs. xtsum

```{r}
bamboo::decompose_numeric(production, select = c("sales", "capital", "labor"), index = "firm")
```

```{r}
xtsum::xtsum(production, variables = c("sales", "capital", "labor"), id = "firm", t = "year", na.rm = TRUE)
```